Random Matrix Theory Tools for the Analysis of Functional Magnetic Resonance Imaging Examinations

### 2022-11-01 paper/paper/SPIE/article.tex
[WIP]

This means that if we examine a system and find that the distribution of eigenvalues of that system
resemble some RMT predicted spectrum, we potentially gain insight into the nature of that system.
If, in addition, we find a large deviance from the spectrum predicted by RMT, we find contrapositive
evidence that the system is \textit{not} like those described by RMT. Roughly, systems
well-described by RMT are highyl random and independent, whereas systems that are not so
well-described are either highly dependent, non-random, or both.

>>>>

This means that if we examine a system and find that the distribution of eigenvalues of that system
resemble some RMT predicted spectrum, we potentially gain insight into the nature of that system.
If, in addition, we find a large deviance from the spectrum predicted by RMT, we find contrapositive
evidence that the system is \textit{not} like those described by RMT. Roughly, complex systems
well-described by RMT are highly random and independent, whereas systems that are not so
well-described are either highly dependent, non-random, or both.

In this sense, RMT has considerable \textit{explanatory} and \textit{statistical} value: the more we
see that a system resembles an RMT system, the less we can distinguish it from one of random,
non-interacting components, and the less the system resembles an RMT system, the more
fundamentally complex and interactive the interactions.

For a system as complex as the human brain, RMT is thus tantalizing. It would be quite something
if we could extract some matrix reduction of brain activity, and if the RMT description of this
matrix either aligned nicely with RMT theory, or otherwise was broadly predictively useful.
